---
title: "README"
author: "Robin Linacre"
date: "30 April 2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Hierarchical bubble

A hierarchical bubble chart HTML Widget for R implemented in d3v4.

This is work in progress, but you can find a working example of a Shiny app [within the repo](https://github.com/RobinL/hierarchical_bubble_r_html_widget/blob/master/example.R).

## Instructions

The widget expects data in the following format (showing first few rows only):

```{r, echo=FALSE}
df <- hierarchicalbubble::generate_test_data()[1:2,]

names <- paste0("cat_", 1:4)
df_l <- hierarchicalbubble::wide_to_long_hierarchy(df,names, "val")
knitr::kable(df_l, options=list(scrollX = TRUE))
```

However, you're more likely to have data that looks like this (first few rows only):

```{r, echo=FALSE}
df <- hierarchicalbubble::generate_test_data()[1:3,]
knitr::kable(df)
```

So a convenience function is provided that converts between the two:

```{r, eval=FALSE}

df <- hierarchicalbubble::generate_test_data()[1:5,]
names <- paste0("cat_", 1:4)

df_l <- hierarchicalbubble::wide_to_long_hierarchy(df,names, "val")
```

To see your visualisation use 

```{r, eval=FALSE}
hierarchicalbubble::hierarchical_bubble(df_l)
```

Here's a screenshot of the widget embedded in a Shiny app:
Screenshot](http://i.imgur.com/AdHQHtX.png)